---
title: "615Midterm_Project"
author: "Qianhui Rong"
date: "10/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Contribution:
##Fionnuala: getting Celtics attendance data, shiny app, EDA writing and editting
##Qianhui: merging Redsox data, Redsox EDA and plots, shiny app 
##Yaotang: getting Redsox data, Celtics EDA, shiny app
##Yifeng: getting Celtics data, Celtics EDA, shiny app

```{r}
#List all libraries needed
library(ggplot2)
library(dplyr)
library(tidyverse)
library(lubridate)
```

##BASEBALL REDSOX
#First Part: Merging Redsox attendance data with Weather data by the key of data
```{r}
#Import all data files needed (In excel, a column of year has already been added)
weather_data <- read.csv("weather.csv")
redsox12 <- read.csv("redsox12.csv")
redsox13 <- read.csv("redsox13.csv")
redsox14 <- read.csv("redsox14.csv")
redsox15 <- read.csv("redsox15.csv")
redsox16 <- read.csv("redsox16.csv")
redsox17 <- read.csv("redsox17.csv")

#Combine redsox data
redsox_whole <- rbind(redsox12,redsox13,redsox14,redsox15,redsox16,redsox17)

#Join the year column and the date column into one
date_mdy <- stringr::str_c(redsox_whole$Year,redsox_whole$Date,sep=",")
redsox_whole$date_mdy <- date_mdy #Add a new column into our data

#Change the format of date_mdy
redsox_whole$Date <- as.Date(redsox_whole$date_mdy, "%Y,%A, %b %d")

#Add a weekday column
redsox_whole$weekday <- weekdays(redsox_whole$Date)

#Deleting all away games
atinredsox <- which(redsox_whole$X.1 == "@")
new_redsox <- redsox_whole[-atinredsox,] #the new data
new_redsox %>% select(Date,Opp,Attendance,weekday)->new2_redsox

#AWND: average daily wind speed data
weather_data %>% select(DATE,AWND,PRCP,TMAX,TMIN) %>% mutate(ATEM=(TMAX+TMIN)/2)->weather_new
weather_new$Date <- weather_new$DATE
weather_new$Date <- as.Date(weather_new$DATE,'%Y-%m-%d')

#Join the two datas
merged <- left_join(new2_redsox,weather_new,by="Date")
```

#Second Part: draw weather plots
```{r}
#Find quarters of percipitation to have better understanding
summary(merged$PRCP) #1st Qu.:0; 2nd Qu.:0; 3rd Qu.:0.02
merged$PRCP_gp <- ifelse(merged$PRCP==0,"Low",
                         ifelse(merged$PRCP>0 & merged$PRCP<0.02, "Medium", "High"))
#Boxplot of PRCP
#Attention that Attendance data is not numeric 
ggplot(merged,aes(x=PRCP_gp,y=as.numeric(Attendance)))+
  geom_boxplot(outlier.colour="black")

#Scatter plot of ATEM
ggplot(merged,aes(x=ATEM,y=as.numeric(Attendance),color=PRCP_gp))+
  geom_point()
ggplot(merged,aes(x=ATEM,y=as.numeric(Attendance),color=PRCP_gp))+
  geom_point()+facet_wrap(~PRCP_gp)

#Scatter plot and line of AWND
ggplot(merged, aes(x=AWND,y=as.numeric(Attendance)))+geom_point()
```
The boxplot illustrating percipitation level and attendance shows that when the percipitation level is high , the average attendance is lower, but when the percipitation level is low or medium, the difference of attendance is not evident. The graph shoes that attendance and percipitation do not directly corrolate, which is different from our expectations, as baseball is played outside. 

The scatter plot shows the relationship between average temperature and attendance number, with subgroups of percipitation groups. Our expected negative relationship between temperature and attendance is not confirmed, possibly because this range of average temperature is in people's confortable zone. With the scatters of different colors, we can see that there are more data on Low and High percipitation groups.

The scatter plot of average wind speed does show a clear positive relationship between wind speed and attendance. 


#Third Part: Think about the opponents and the attendance amount
We estimate that when Redsox's opponent is a strong one or a famous one, like New York Yankees, the attendance should be higher, and for those with less familiarity, the attendance amount should be lower.

```{r}
ggplot(merged,aes(x=Opp,y=as.numeric(Attendance)))+geom_bar(aes(y = (..count..)/sum(..count..)))
```
For the opponents'bar chart, we can see that when the Redsox's opponent is BAL, NYY, TBR or TOR, the attendance amount tends to be higher than the others. As many of these teams come from nearby regions, it is also possible that fans of the opposing team were able to attend the game, increasing attendance. 

#Forth Part: Considering the strength of the team
As a strong team is likely to draw more fans, we researched the team's sucess for the years in question, and placed them on a three point scale. According to our research, we've made a audience's emotion chart the concerned years(2012-2017). We determined the emotion chart as follows: and a sad face=1, an adequate (ok) face=2, a happy face=3:
2012: Sad face 
2013: Happy face 
2014: Sad face 
2015: Sad face
2016: Adequate face
2017: Adequate face

The 2012 season was considered a "sad face" as they ended up ranking last in their devision. The following year was a "happy face" because the team won the world series, the highest possible award in the sport. The following two years they again ranked as the worst team in their devision. The 2016 and 2017 seasons were adequate as they were ranked first in their devision.

It should also be noted that the Boston Marathon Bombing occured in the 2013 season. The team honored many first responders during the games, and we expected a higher level of attendance that year due to the need to increase moral accross the city. 

```{r}
library(lubridate)
#Create a variable of audience's emotion
merged$face_gp <- ifelse(year(merged$Date)==2012,1,
                         ifelse(year(merged$Date)==2013,3,
                                ifelse(year(merged$Date)==2014,1,
                                       ifelse(year(merged$Date)==2015,1,
                                              ifelse(year(merged$Date)==2016,2,
                                                     ifelse(year(merged$Date)==2017,2,0))))))
#Plot emotion and attendance
ggplot(merged,aes(x=as.numeric(face_gp),y=as.numeric(face_gp)))+geom_bar(aes(y = (..count..)/sum(..count..))) + labs(x = "Team Performance", y = "Proportion of All Attendance")
```
The plot shows exactly the opposite of our expectation. A great year had smaller proportion of attendance and a poor year has a larger proportion. This may be because our research results on determining the emotion variable is not efficient, and three categories were not enough to capture the nuances of what makes a season "good. It is also hard to scale with only three emotions after such a win as the world series, which cannot compare to winning their devision, which is a great achievement in and of itself. It is also possible that our sample size was not large enough. There was only one year that was considered great, which is not able to capture this trend long term. It should also be noted that in the previous year the team was ranked last in their devision. Fans could have assumed that their performance would not have imoproved, and therefore were less likely to purchase tickets. This logic could have followed, and following a good or great year, more people bough tickets in the hopes of a repeat performance. 

##BASKETBALL CELTICS
#First Part:Getting data from websites and merging Celtics attendance data with eeather data by the key of data
```{r}
library(readxl)

weather_data <- read.csv("weather.csv")
date<-read.csv('date.csv')
reduce_date<-date[1:328,]
home_date <- reduce_date[-which(reduce_date$X.2 == "@")] 
```

```{r}
library(XML)
library(tidyverse)
library(RCurl)
library(rvest)
library(stringr)
library(dplyr)
games <- c("http://www.espn.com/nba/game?gameId=400277737", "http://www.espn.com/nba/game?gameId=400277774", "http://www.espn.com/nba/game?gameId=400277790", "http://www.espn.com/nba/game?gameId=400277830", "http://www.espn.com/nba/game?gameId=400277851", "http://www.espn.com/nba/game?gameId=400277881", "http://www.espn.com/nba/game?gameId=400277893", "http://www.espn.com/nba/game?gameId=400277931", "http://www.espn.com/nba/game?gameId=400277945", "http://www.espn.com/nba/game?gameId=400277979",
"http://www.espn.com/nba/game?gameId=400278005", "http://www.espn.com/nba/game?gameId=400278035", "http://www.espn.com/nba/game?gameId=400278090", "http://www.espn.com/nba/game?gameId=400278102", "http://www.espn.com/nba/game?gameId=400278188", "http://www.espn.com/nba/game?gameId=400278203", "http://www.espn.com/nba/game?gameId=400278239", "http://www.espn.com/nba/game?gameId=400278251", "http://www.espn.com/nba/game?gameId=400278277", "http://www.espn.com/nba/game?gameId=400278293", "http://www.espn.com/nba/game?gameId=400278304", "http://www.espn.com/nba/game?gameId=400278350", "http://www.espn.com/nba/game?gameId=400278372", "http://www.espn.com/nba/game?gameId=400278392", "http://www.espn.com/nba/game?gameId=400278406", "http://www.espn.com/nba/game?gameId=400278425", "http://www.espn.com/nba/game?gameId=400278453", "http://www.espn.com/nba/game?gameId=400278474", "http://www.espn.com/nba/game?gameId=400278498", "http://www.espn.com/nba/game?gameId=400278587", "http://www.espn.com/nba/game?gameId=400278637", "http://www.espn.com/nba/game?gameId=400278679", "http://www.espn.com/nba/game?gameId=400278700", "http://www.espn.com/nba/game?gameId=400278718", "http://www.espn.com/nba/game?gameId=400278774", "http://www.espn.com/nba/game?gameId=400278795", "http://www.espn.com/nba/game?gameId=400278835", "http://www.espn.com/nba/game?gameId=400278847", "http://www.espn.com/nba/game?gameId=400278867", "http://www.espn.com/nba/game?gameId=400278888",
"http://www.espn.com/nba/game?gameId=400488897", "http://www.espn.com/nba/game?gameId=400488937", "http://www.espn.com/nba/game?gameId=400488974", "http://www.espn.com/nba/game?gameId=400488986", "http://www.espn.com/nba/game?gameId=400489001", "http://www.espn.com/nba/game?gameId=400489052",
"http://www.espn.com/nba/game?gameId=400489090", "http://www.espn.com/nba/game?gameId=400489105",
"http://www.espn.com/nba/game?gameId=400489135", "http://www.espn.com/nba/game?gameId=400489156", "http://www.espn.com/nba/game?gameId=400489192", "http://www.espn.com/nba/game?gameId=400489206", "http://www.espn.com/nba/game?gameId=400489231", "http://www.espn.com/nba/game?gameId=400489246", "http://www.espn.com/nba/game?gameId=400489266", "http://www.espn.com/nba/game?gameId=400489309", "http://www.espn.com/nba/game?gameId=400489333", "http://www.espn.com/nba/game?gameId=400489357", "http://www.espn.com/nba/game?gameId=400489429", "http://www.espn.com/nba/game?gameId=400489442", "http://www.espn.com/nba/game?gameId=400489459", "http://www.espn.com/nba/game?gameId=400489509", "http://www.espn.com/nba/game?gameId=400489531", "http://www.espn.com/nba/game?gameId=400489551", "http://www.espn.com/nba/game?gameId=400489582", "http://www.espn.com/nba/game?gameId=400489616", "http://www.espn.com/nba/game?gameId=400489631", "http://www.espn.com/nba/game?gameId=400489653", "http://www.espn.com/nba/game?gameId=400489727", "http://www.espn.com/nba/game?gameId=400489750", "http://www.espn.com/nba/game?gameId=400489780", "http://www.espn.com/nba/game?gameId=400489793", "http://www.espn.com/nba/game?gameId=400489810", "http://www.espn.com/nba/game?gameId=400489835", "http://www.espn.com/nba/game?gameId=400489848", "http://www.espn.com/nba/game?gameId=400489882", "http://www.espn.com/nba/game?gameId=400489936", "http://www.espn.com/nba/game?gameId=400489970", "http://www.espn.com/nba/game?gameId=400490006", "http://www.espn.com/nba/game?gameId=400490051", "http://www.espn.com/nba/game?gameId=400490095", "http://www.espn.com/nba/game?gameId=400578298", "http://www.espn.com/nba/game?gameId=400578351", "http://www.espn.com/nba/game?gameId=400578351", "http://www.espn.com/nba/game?gameId=400578366", "http://www.espn.com/nba/game?gameId=400578403", "http://www.espn.com/nba/game?gameId=400578417", "http://www.espn.com/nba/game?gameId=400578440", "http://www.espn.com/nba/game?gameId=400578486", "http://www.espn.com/nba/game?gameId=400578515", "http://www.espn.com/nba/game?gameId=400578533", "http://www.espn.com/nba/game?gameId=400578557", "http://www.espn.com/nba/game?gameId=400578571", "http://www.espn.com/nba/game?gameId=400578586", "http://www.espn.com/nba/game?gameId=400578623", "http://www.espn.com/nba/game?gameId=400578663", "http://www.espn.com/nba/game?gameId=400578677", "http://www.espn.com/nba/game?gameId=400578724", "http://www.espn.com/nba/game?gameId=400578767", "http://www.espn.com/nba/game?gameId=400578778", "http://www.espn.com/nba/game?gameId=400578802", "http://www.espn.com/nba/game?gameId=400578855", "http://www.espn.com/nba/game?gameId=400578872", "http://www.espn.com/nba/game?gameId=400578883", "http://www.espn.com/nba/game?gameId=400578990", "http://www.espn.com/nba/game?gameId=400579008", "http://www.espn.com/nba/game?gameId=400579025", "http://www.espn.com/nba/game?gameId=400579042", "http://www.espn.com/nba/game?gameId=400579081", "http://www.espn.com/nba/game?gameId=400579136", "http://www.espn.com/nba/game?gameId=400579151", "http://www.espn.com/nba/game?gameId=400579172", "http://www.espn.com/nba/game?gameId=400579190", "http://www.espn.com/nba/game?gameId=400579246", "http://www.espn.com/nba/game?gameId=400579261", "http://www.espn.com/nba/game?gameId=400579284", "http://www.espn.com/nba/game?gameId=400579335", "http://www.espn.com/nba/game?gameId=400579356", "http://www.espn.com/nba/game?gameId=400579387", "http://www.espn.com/nba/game?gameId=400579407", "http://www.espn.com/nba/game?gameId=400579421", "http://www.espn.com/nba/game?gameId=400579486",
"http://www.espn.com/nba/game?gameId=400579506", "http://www.espn.com/nba/game?gameId=400827892", "http://www.espn.com/nba/game?gameId=400827911", "http://www.espn.com/nba/game?gameId=400827927", "http://www.espn.com/nba/game?gameId=400827963", "http://www.espn.com/nba/game?gameId=400828003", "http://www.espn.com/nba/game?gameId=400828016", "http://www.espn.com/nba/game?gameId=400828055", "http://www.espn.com/nba/game?gameId=400828066", "http://www.espn.com/nba/game?gameId=400828104", "http://www.espn.com/nba/game?gameId=400828116", "http://www.espn.com/nba/game?gameId=400828169", "http://www.espn.com/nba/game?gameId=400828206", "http://www.espn.com/nba/game?gameId=400828223", "http://www.espn.com/nba/game?gameId=400828254", "http://www.espn.com/nba/game?gameId=400828276", "http://www.espn.com/nba/game?gameId=400828298", "http://www.espn.com/nba/game?gameId=400828341", "http://www.espn.com/nba/game?gameId=400828363", "http://www.espn.com/nba/game?gameId=400828382", "http://www.espn.com/nba/game?gameId=400828415", "http://www.espn.com/nba/game?gameId=400828467", "http://www.espn.com/nba/game?gameId=400828482", "http://www.espn.com/nba/game?gameId=400828533", "http://www.espn.com/nba/game?gameId=400828572", "http://www.espn.com/nba/game?gameId=400828585", "http://www.espn.com/nba/game?gameId=400828624", "http://www.espn.com/nba/game?gameId=400828660", "http://www.espn.com/nba/game?gameId=400828679", "http://www.espn.com/nba/game?gameId=400828743", "http://www.espn.com/nba/game?gameId=400828756", "http://www.espn.com/nba/game?gameId=400828773", "http://www.espn.com/nba/game?gameId=400828786", "http://www.espn.com/nba/game?gameId=400828840", "http://www.espn.com/nba/game?gameId=400828852", "http://www.espn.com/nba/game?gameId=400828890", "http://www.espn.com/nba/game?gameId=400828933", "http://www.espn.com/nba/game?gameId=400828944", "http://www.espn.com/nba/game?gameId=400829055", "http://www.espn.com/nba/game?gameId=400829068", "http://www.espn.com/nba/game?gameId=400829092", "http://www.espn.com/nba/game?gameId=400829104")

```

```{r}
celtics_attendance <- vector("numeric", 164)
for (i in 1:length(games)){
  read_html(games[i]) %>%
  html_nodes("#gamepackage-game-information") %>%
  html_text() %>%
  strsplit(split = "\n") %>%
  unlist() %>%
  .[. != ""]  -> n
  str_extract(n, "Attendance: ..,...") -> n1
str_extract(n1, "..,...") -> n2
na.omit(n2)-> n3 #take out comma, then do as.intiger
n4 <- as.integer(gsub(",", "", n3)) 
n4 -> celtics_attendance[i]
}
celtics_attendance
```


```{r}
attendance<-as.data.frame(celtics_attendance)
library(dplyr)
new_attendance<-cbind(attendance,home_date)
celtics<-new_attendance %>% select(Date,celtics_attendance)
celtics$Date<-as.Date(celtics$Date, '%a, %b %d, %Y')
weather_data$Date<-as.Date(weather_data$DATE, '%m/%d/%y')
complete_data<-left_join(celtics,weather_data,by='Date')
reduce_data<-complete_data %>% select(Date,AWND,PRCP,SNOW,TMAX,TMIN,TAVG,celtics_attendance) %>% mutate(ATEM=(TMAX+TMIN)/2)

reduce_data$TAVG[1:36]<-round((reduce_data$TMAX[1:36]+reduce_data$TMIN[1:36])/2)
reduce_data$weekday <- weekdays(reduce_data$Date)
unique(reduce_data$weekday)
#N<-dim(reduce_data)[1]
#for (i in 1:164){
 # if (reduce_data$weekday[i]=='Friday'){reduce_data$type=1}else{reduce_data$type==0}}
reduce_data$type<- ifelse(reduce_data$weekday=='Friday','weekend_game',
                         ifelse(reduce_data$weekday=='Saturday','weekend_game',
                                ifelse(reduce_data$weekday=='Sunday','weekday_game',
                                       ifelse(reduce_data$weekday=='Monday','weekday_game',
                                              ifelse(reduce_data$weekday=='Thursday','weekday_game',
                                                     ifelse(reduce_data$weekday=='Wednesday','weekday_game',
                                                            ifelse(reduce_data$weekday=='Tuesday','weekday_game',0)))))))


```

#Second Part: draw weather plots
```{r}
library(ggplot2)
library(esquisse)
summary(reduce_data$PRCP) #1st Qu.:0; 2nd Qu.:0; 3rd Qu.:0.02
reduce_data$PRCP_gp <- ifelse(reduce_data$PRCP==0,"Low",
                         ifelse(reduce_data$PRCP>0 & reduce_data$PRCP<0.02, "Medium", "High"))

ggplot(data = reduce_data) + aes(y = celtics_attendance, x = PRCP_gp) +
  geom_boxplot(color = "orange") +
  theme_minimal()

ggplot(reduce_data,aes(x=SNOW,y= celtics_attendance,color=PRCP_gp))+
  geom_point()
ggplot(reduce_data,aes(x=SNOW,y= celtics_attendance,color=PRCP_gp))+
  geom_point()+facet_wrap(~PRCP_gp)

#Scatter plot and line of AWND
ggplot(reduce_data, aes(x=AWND,y= celtics_attendance)) + geom_point()

ggplot(reduce_data,aes(x=type,y=celtics_attendance,color=PRCP_gp))+
  geom_boxplot()+facet_wrap(~PRCP_gp)+theme(axis.text.x=(element_text(angle = 15)))

#ggplot(reduce_data,aes(x=PRCP_gp,y=celtics_attendance,color=PRCP_gp))+
 # geom_boxplot()+theme(axis.text.x=(element_text(angle = 15)))
```

1)The boxplot which displays the relationship between percipitation level and attendance reveals that when the percipitation level is high , the average of attendance is relatively higher compare to when the percipitation is medium and low. However, when the percipitation level is low or medium, the difference of attendance is not evident: the minimum of attendance(low) is lower that the minimum of attendance(medium), even though the median of attendance(low) is higher than attendance(medium).This observation is different from our expectations.

2)The scatter plot shows the relationship between attendance and snow, with subgroup of PRCP. We expect that the larger extent of snow would cause less attendance but we find that even the snow is in level 10, the attendance of match could be full. We maybe explain it according to protection of stadium preventing the snow to come in, so that audience does not care about the snow at all. With the scatters of different colors, we can find that percipitation have much more affect on the attendance compare to snow. 

3)The scatter plot of average wind speed does show a clear relationship between wind speed and attendance. 

4)The scatter plot indicate people were more likely to attend a game in the weekday and the range of attendance of games happended at weekend is bigger than weekday. The box plot illustrates the attendance of Celtic games in weekend or weekday, filled in to indicate if the game was played on a heavy rainy day or not. To be honest, we supoosed that people were more likely to attend a game at weekend due to they did not have school or work the next day, assuming a traditional schedule, and that this could possibly overcome undesirable weather. However, the box plot show a unexpected result. Examination of the graph shows that games played on weekdays do not reduce attendance. The game played at weekday on average have a higher attendance than at weekend in a high level of precipitation. Additionally, the games that have the lowest attendance are played on dry days at weekend. Our belief that weekends will overcome bad weather is disproved. Meanwhile, we can see that games played on weekends have a greater range of attendance form the box plot. It probobly caused by basketball is played indoors, we expected it to have a weaker effect on attendance than it would on baseball.


#Fifth Part: Shiny App
```{r}

library(shiny) # load the shiny package

# Define UI for application
ui <- shinyUI(fluidPage(
  
  # Header or title Panel 
  titlePanel(h4('Attendance at Sporting Events', align = "center")),
  
  # Sidebar panel
  sidebarPanel(
    
    
    
    selectInput("var", label = "1. Select the quantitative Variable", 
                choices = c("Baseball" = 1, "Basketball" = 2),
                selected = 1), 
    
    
    sliderInput("bin", "2. Select the number of histogram BINs by using the slider below", min=5, max=25, value=15)
    
    
  ),
  
  # Main Panel
  mainPanel(
    textOutput("text1"),
    textOutput("text2"),
    plotOutput("myhist")
    
  )
  
)
)
library(shiny) # Load shiny package
redsox12 <- read.csv("redsox12.csv")
redsox13 <- read.csv("redsox13.csv")
redsox14 <- read.csv("redsox14.csv")
redsox15 <- read.csv("redsox15.csv")
redsox16 <- read.csv("redsox16.csv")
redsox17 <- read.csv("redsox17.csv")

#Combine redsox data
redsox_whole <- rbind(redsox12,redsox13,redsox14,redsox15,redsox16,redsox17)


shinyServer(
  
  
  server <- function(input, output) {
    
    output$text1 <- renderText({ 
      colm = as.numeric(input$var)
      paste("Data set variable/column name is", names(redsox_whole[colm]))
      
    })
    
    output$text3 <- renderText({ 
      paste("Number of histogram BINs is", input$bin)
    })
    
    output$myhist <- renderPlot(
      
      {
        colm = as.numeric(input$var)
        hist(redsox_whole[,colm], col =input$colour, xlim = c(2000, max(redsox_whole[,colm])), main = "Histogram of Baseball Attendance", breaks = seq(0, max(redsox_whole[,colm]),l=input$bin+1), xlab = names(redsox_whole[colm]))}
      
    )    
  }
)

# Run the application 
shinyApp(ui = ui, server = server)
```

```


